### 2021-03-29 README.Rmd
FURTHER UPDATES TO README

# berchukHaulout

This repository contains the data and code for our paper:
*Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas*

@@

### NOAA License

Software code created by U.S. Government employees is not subject to copyright in the United States (17 U.S.C. §105). The United States/Department of Commerce reserve all rights to seek and obtain copyright protection in countries other than the United States for Software authored in its entirety by the Department of Commerce. To this end, the Department of Commerce hereby grants to Recipient a royalty-free, nonexclusive license to use, copy, and create derivative works of the Software outside of the United States.

>>>>

## Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas
Josh M. London^1^,✉, Paul B. Conn^1^, Stacie K. Hardy^1^, Erin L. Richmond^1^, Jay M. Ver Hoef^1^, Irina S. Trukhanova^1^, Michael F. Cameron^1^, and Peter L. Boveng^1^
1 Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
✉ Correspondence: Josh M. London <josh.london@noaa.gov>

This repository contains the research compendium in support of the above titled paper.
The manuscript is currently in preparation and the text, code, analysis, and results
are under active development.

@@
